---
Classification: Predict Customer's Brand Preference
title: "2BrandPreferencePrediction_Caret_ClassificationModels"
author: "SuninChoi"
date: "12/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Brand Preference Prediction


```{r data importing and libraries, echo=FALSE}
BelkinElagoComplete <- read.csv2("C:/Users/sunny/Desktop/2.R/5. BrandPreferencePrediction/Brand Preference Prediction with R/data/BelkinElagoComplete.csv")
belcom <- BelkinElagoComplete

SurveyIncomplete <- read.csv("C:/Users/sunny/Desktop/2.R/5. BrandPreferencePrediction/Brand Preference Prediction with R/data/SurveyIncomplete.csv")
belincom <- SurveyIncomplete

library(ggplot2)
library(lattice)
library(caret)
require("devtools")
library(recipes)
library(C50)
library(rpart)
library(rpart.plot)
library(party)
library(matrixStats)
library(funModeling)
library(Hmisc)
library(corrplot)
library(PerformanceAnalytics)
library(RColorBrewer)
library(dplyr)
```


### Exploration 1. initial check up of complete and incomplete data


```{r initial checking up, echo=FALSE}
df_status(belcom)
df_status(belincom)

str(belcom)
str(belincom)

plot_num(belcom)
plot_num(belincom)

summary(belcom)
summary(belincom)

# Change data types
belcom$elevel <- as.factor(belcom$elevel)
belcom$car <- as.factor(belcom$car)
belcom$zipcode <- as.factor(belcom$zipcode)
belincom$elevel <- as.factor(belincom$elevel)
belincom$car <- as.factor(belincom$car)
belincom$zipcode <- as.factor(belincom$zipcode)

table(is.na(belcom))
table(is.na(belincom))
belcom$elevel <- as.numeric(belcom$elevel)
belcom$car <- as.numeric(belcom$car)
belcom$zipcode <- as.numeric(belcom$zipcode)
belincom$elevel <-as.numeric(belincom$elevel)
belincom$car <- as.numeric(belincom$car)
belincom$zipcode <- as.numeric(belincom$zipcode)

freq(belcom$car)
freq(belincom$car)

```


### Exploration 2. Distributions
1) Categorical features
table(belcom$salary)
Bar plots
2) Numerical feaetures
Histogram


```{r data distributions, echo=FALSE}

# Correlation matrix
correlation_table(belcom, "brand")
var_rank_info(belcom, "brand")
## salary, credit, age

ctbelincom <- rcorr(as.matrix(belincom))
ctbelincom

```


### 3. Model building with caret
building a model using 
1)Gradient Boosted Trees, 2)a decision tree, C5.0, 3) Radom Forest

1. develop a working 'pipeline'
(including data splitting, pre-processing, feature selection
model tuning using resampling, variable importance estimation)


```{r developing a pipeline, echo=FALSE}
# createDataPartition: spliting the data into two groups
set.seed(889)
trainbelcom <- createDataPartition (y = belcom$brand, p = .75, list = FALSE)
str(trainbelcom)

traindata <- belcom[trainbelcom,]
testdata <- belcom[-trainbelcom,]

belcomcontrol <- trainControl(method = "repeatedcv", 
                           number = 10, repeats = 1)

```



2. Gradient Boosting Trees

```{r gbm}
gbmGrid <- expand.grid(interaction.depth = 3,
                       n.trees = 150,
                       shrinkage = 0.1,
                       n.minobsinnode = 10)
nrow(gbmGrid)

Final_gbmbel <- train(brand ~ ., 
                   data = traindata, 
                   preProc = c("center", "scale"),
                   method = "gbm", 
                   trControl = belcomcontrol, 
                   verbose = FALSE, 
                   tuneGrid = gbmGrid)
Final_gbmbel

# Accuracy   Kappa    
# 0.7863985  0.5765373



```



3. Decision Tree, C5.0 with 10-fold cross validation and 
an Automatic Tuning Grid with a tuneLength of 2

```{r decision tree, echo=FALSE}
dtree_belcom <- train(brand~., 
                      data = traindata, 
                      preProc = c("center", "scale"),
                      method = "rpart", 
                      trControl=belcomcontrol, 
                      tuneLength = 8)
dtree_belcom

rpbelcom <- rpart(brand~., data = traindata, 
                  method = 'class')
rpart.plot(rpbelcom, extra = 100)

# make a prediction
predict_Finalrpbelcom <- predict(Finalrpbelcom, testdata, type = 'class')
# measure performance
table_Finalrpbelcom <- table(testdata$brand, predict_Finalrpbelcom)
table_Finalrpbelcom
accuracy_Test <- sum(diag(table_Finalrpbelcom)) / sum(table_Finalrpbelcom)
print(paste('accuracy for test', accuracy_Test))

```


4. Random Forest with 10-fold cross validation 
   w/ manually tune 5 different mtry values

```{r random forest, echo=FALSE}
rfbel <- train(brand~., 
               data = traindata, 
               preProc = c("center", "scale"),
               method = "rf", 
               trControl=belcomcontrol,
               tuneLength = 5)
rfbel

rfGrid <-  expand.grid(mtry = 9)
rfbelcom <- train(brand~., 
                  data = traindata, 
                  preProc = c("center","scale"),
                  method = "rf",  
                  trControl=belcomcontrol,
                  tuneGrid = rfGrid)
rfbelcom

# Accuracy   Kappa   
# 0.7810709  0.563555

varImp(rfbelcom, scale = FALSE) 
varImp(rfbelcom, scale = FALSE, importance = TRUE)

```


5. Resampling distributions

```{r resampling distributions}
# exploring and comparing resampling distributions

resamps <- resamples(list(GBM = Final_gbmbel, DT = dtree_belcom, RF = rfbelcom))
resamps
summary(resamps)

predict_Final <- predict(dtree_belcom, belincom, type = 'raw')

```


